---
title: "R Notebook"
author: "Sang Yoon (Andy) Hwang"
date: 2019-02-06
output:
  html_document: default
  html_notebook: default
---

**Principles of Data Visualization and Introduction to ggplot2**

I have provided you with data about the 5,000 fastest growing companies in the US, as compiled by Inc. magazine. lets read this in:

```{r}

library(sqldf)
library(ggplot2)
library(outliers)

inc <- read.csv("https://raw.githubusercontent.com/charleyferrari/CUNY_DATA_608/master/module1/Data/inc5000_data.csv", header= TRUE)

```

And lets preview this data:

```{r}

head(inc)

```
```{r}

summary(inc)

```

Think a bit on what these summaries mean. Use the space below to add some more relevant non-visual exploratory information you think helps you understand this data:

Let's find some outliers (notably Growth, employees and Revenue; maximum values are way too high) in our data. 
Not only that, let's see data types for each column and remove scientific notations in summary.

```{r}

# Insert your code here, create more chunks as necessary

#Outliers
max_growth <- subset(inc, Growth_Rate == max(inc['Growth_Rate']))
max_growth

max_rev <- subset(inc, Revenue == max(inc['Revenue']))
max_rev

max_employee <- subset(inc, inc['Employees'] == 66803)
max_employee

#Let's see how data looks like without outliers.
inc_no_outlier <- subset(inc, !(Rank %in% c(max_growth['Rank'], max_rev['Rank'], max_employee['Rank'])) )
summary(inc_no_outlier)
#Well, it seems like data is still heavily right-skewed as Employees, Revenue and Growth rate have much higher Mean than Median even after removing outliers.

#Data types for each column
str(inc)

# Using scipen=999 to disable scientific notations in Revenue.
options(scipen=999)
summary(inc)
```

## Question 1

Create a graph that shows the distribution of companies in the dataset by State (ie how many are in each state). There are a lot of States, so consider which axis you should use. This visualization is ultimately going to be consumed on a 'portrait' oriented screen (ie taller than wide), which should further guide your layout choices.

```{r, warning=FALSE, fig1, fig.height = 10, fig.width=10}

# Answer Question 1 here

# I am using sqldf to group by State and count number of companies
query<-sqldf("select 
          State, count(distinct Name) as cnt_comp
          from inc 
          group by State")

# Using ggplot to graph
ggplot(query, aes(x=reorder(State, cnt_comp), y=cnt_comp)) +
 geom_bar(stat="identity", fill="green") +
 geom_text(aes(label=cnt_comp)) +
 ylab("# of companies") +
 xlab("State") +
 coord_flip() +
 ggtitle("Number of Companies by State") +
 theme_bw() 

```

## Quesiton 2

Lets dig in on the state with the 3rd most companies in the data set. Imagine you work for the state and are interested in how many people are employed by companies in different industries. Create a plot that shows the average and/or median employment by industry for companies in this state (only use cases with full data, use R's `complete.cases()` function.) In addition to this, your graph should show how variable the ranges are, and you should deal with outliers.

```{r, warning=FALSE, fig2, fig.height = 10, fig.width=10}

# Answer Question 2 here

#Filter out N/As in full data
full <- inc[complete.cases(inc),]

#Using filtered full, choose 3rd most state
third <- subset(full, State == 'NY')

#The summary looks good, no N/As
summary(third)


# I am using sqldf to group by industry to get mean employment in NY
query<-sqldf("select 
          Industry, avg(Employees) as avg_emp
          from third 
          group by Industry")

# Using ggplot to graph
ggplot(query, aes(x=reorder(Industry, avg_emp), y=round(avg_emp,0))) +
 geom_bar(stat="identity", fill="skyblue") +
 geom_text(aes(label=round(avg_emp,0))) +
 ylab("Mean Number Of Employees") +
 xlab("Industry") +
 ggtitle("Mean Number of Employees by Industry in New York") +
 coord_flip() +
 theme_bw() 

#There are outliers in Employees variables by Industry. We will get rid of these and re-graph our result.
ggplot(third, aes(x=reorder(Industry,Employees) , y=Employees)) +
  geom_boxplot() +
  ggtitle("Box-Plot by Industry and number of Employees") +
  coord_flip()

#outlierKD function will automatically detect outliers and replace dataset (third) with dataset without outliers
outlierKD <- function(dt, var) {
     var_name <- eval(substitute(var),eval(dt))
     na1 <- sum(is.na(var_name))
     m1 <- mean(var_name, na.rm = T)
     par(mfrow=c(2, 2), oma=c(0,0,3,0))
     boxplot(var_name, main="With outliers")
     hist(var_name, main="With outliers", xlab=NA, ylab=NA)
     outlier <- boxplot.stats(var_name)$out
     mo <- mean(outlier)
     var_name <- ifelse(var_name %in% outlier, NA, var_name)
     boxplot(var_name, main="Without outliers")
     hist(var_name, main="Without outliers", xlab=NA, ylab=NA)
     title("Outlier Check", outer=TRUE)
     na2 <- sum(is.na(var_name))
     cat("Outliers identified:", na2 - na1, "n")
     cat("Propotion (%) of outliers:", round((na2 - na1) / sum(!is.na(var_name))*100, 1), "n")
     cat("Mean of the outliers:", round(mo, 2), "n")
     m2 <- mean(var_name, na.rm = T)
     cat("Mean without removing outliers:", round(m1, 2), "n")
     cat("Mean if we remove outliers:", round(m2, 2), "n")
     dt[as.character(substitute(var))] <- invisible(var_name)
     assign(as.character(as.list(match.call())$dt), dt, envir = .GlobalEnv)
     cat("Outliers successfully removed", "n")
     return(invisible(dt))
}

#Using loop, remove outliers in Employees by each industry
industries <- unique(third$Industry)
third_wo <-NULL

for (i in industries){
  d2 <- subset(third, Industry == i)
  outlierKD(d2, Employees)
  third_wo <- rbind(d2, third_wo)
}

# Now, dataset (third) is free of outliers but notice there are NAs because these NAs were outliers before
summary(third)
summary(third_wo)

# We want to filter out N/As in third without outliers once more
third_wo <- third_wo[complete.cases(third_wo),]

#Let's see how box-plot now looks like with new dataset. Pretty neat
ggplot(third_wo, aes(x=reorder(Industry,Employees) , y=Employees)) +
  geom_boxplot() +
  ggtitle("Box-Plot by Industry and Number of Employees") +
  coord_flip()



# I am re-using sqldf to group by industry to get mean employment in NY (without outliers)
query<-sqldf("select 
          Industry, avg(Employees) as avg_emp
          from third_wo 
          group by Industry")

# Using ggplot to re-graph (without outliers)
ggplot(query, aes(x=reorder(Industry, avg_emp), y=round(avg_emp,0))) +
 geom_bar(stat="identity", fill="skyblue") +
 geom_text(aes(label=round(avg_emp,0))) +
 ylab("Mean Number Of Employees") +
 xlab("Industry") +
 ggtitle("Mean Number of Employees by Industry in New York") +
 coord_flip() +
 theme_bw() 

# Use query again
query <- sqldf("select 
          Industry, avg(Employees) as avg_emp
          from third 
          group by Industry")
 
# We can also remove outliers in mean level
outlier_avg <- outlier(query$avg_emp)

# remove a row with outlier
query <- subset(query, avg_emp != outlier_avg)

# Graph again
ggplot(query, aes(x=reorder(Industry, avg_emp), y=round(avg_emp,0))) +
 geom_bar(stat="identity", fill="skyblue") +
 geom_text(aes(label=round(avg_emp,0))) +
 ylab("Mean Number Of Employees") +
 xlab("Industry") +
 ggtitle("Mean Number of Employees by Industry in New York") +
 coord_flip() +
 theme_bw() 


```

## Question 3

Now imagine you work for an investor and want to see which industries generate the most revenue per employee. Create a chart that makes this information clear. Once again, the distribution per industry should be shown.

```{r, warning=FALSE, fig3, fig.height = 10, fig.width=10}
# Answer Question 3 here

# Use query again
query<-sqldf(
          "SELECT a.Industry, (tot_rev / emp_cnt) as rev_emp
          FROM
          (select 
          Industry, SUM(Revenue) as tot_rev, SUM(Employees) as emp_cnt
          from full 
          group by Industry) as a"
)

#Set K = 4 for K-mean clustering: Very high, high, medium, low by Revenue Per Employee
cl=(kmeans(query$rev_emp,4))

#set cluster as a factor and add it to our dataset
query$cluster=factor(cl$cluster)
centers=as.data.frame(cl$centers)

#Plot cluster points
ggplot(query, aes(x=reorder(Industry, rev_emp), y=round(rev_emp,2), color=cluster)) +
 geom_point() + 
 geom_text(aes(label=round(rev_emp/1000,2)), hjust=1, size=4) +
 ylab("Revenue Per Employee (1000's)") +
 xlab("Industry") +
 ggtitle("K-Mean Clustering : Revenue Per Employee") +
 coord_flip() +
 theme_bw() +
 scale_y_continuous(labels = function(x){paste0(x/1000, 'K')})

```